Lessons learned: creating tutorials to teach agent-based modelling to archaeologists

### 2025-07-24 paper.Rmd
minor updates after recommendation by PCI Archaeo (https://doi.org/10.24072/pci.archaeo.100596).

We thank our two reviewers Dries Daems and Andreas Angourakis for their valuable comments and suggestions that have improved this paper. We thank James Allison for his rol as recommender for PCI Archaeology, contributing to enhancing the quality of the paper.

>>>>

We thank our two reviewers Dries Daems and Andreas Angourakis for their valuable comments and suggestions that have improved this paper. We thank James Allison for his rol as recommender for PCI Archaeology, contributing to enhancing the quality of the paper [@allison2025]. A preprint version of this article has been peer-reviewed and recommended by PCI Archaeo (<https://doi.org/10.24072/pci.archaeo.100596>).

### 2025-07-24 paper.tex
minor updates after recommendation by PCI Archaeo (https://doi.org/10.24072/pci.archaeo.100596).

\title{Lessons learned: creating tutorials to teach agent-based modelling to archaeologists}
\author{}
\date{\vspace{-2.5em}June 20, 2025}

@@

We thank our two reviewers Dries Daems and Andreas Angourakis for their valuable comments and suggestions that have improved this paper. We thank James Allison for his rol as recommender for PCI Archaeology, contributing to enhancing the quality of the paper.

@@

>>>>

\title{Lessons learned: creating tutorials to teach agent-based modelling to archaeologists}
\author{}
\date{\vspace{-2.5em}July 24, 2025}

@@

We thank our two reviewers Dries Daems and Andreas Angourakis for their valuable comments and suggestions that have improved this paper. We thank James Allison for his rol as recommender for PCI Archaeology, contributing to enhancing the quality of the paper (Allison 2025). A preprint version of this article has been peer-reviewed and recommended by PCI Archaeo (\url{https://doi.org/10.24072/pci.archaeo.100596}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-allison2025}{}}%
Allison, J. 2025 Open Educational Resources for Agent-Based Modeling in Archaeology. \emph{Peer Community in Archaeology} 1: 100596. DOI: https://doi.org/\href{https://doi.org/10.24072/pci.archaeo.100596}{10.24072/pci.archaeo.100596}.
